---
title: "Analyses"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache=T, rows.print=20)
options(digits=2, width=260, scipen=999)
```

 - Here you can find the code and the results of all main analyses. 
 - To see the code, click on button "Code".
 - Alternatively, you can download the rmd file from the github repo.

# Set-up

Load packages & workspace.

```{r r-setup, results='hide', cache=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
packages <- c("broom.mixed", "brms", "corrr", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", "PerFit", "performance", "psych", 
              "quanteda.textstats", "scales", "semTools", "tidyverse")

# load packages
lapply(c(packages, "td"), library, character.only = TRUE)

# load workspace
load("data/workspace_1.RData")
```

# Measures

Let's first inspect the individual measures, how they develop over time. For positive and negative affect, we also look at their factor structure, as they're measured with multiple items.

## Well-being
### Life satisfaction

Let's inspect the development of life satisfaction across the study. We nest reponses inside participants and waves to get better results.

```{r}
fit_life_sat <- lmer(life_sat ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(fit_life_sat)
dat_fig_life_sat <- data.frame(type = "Life satisfaction", dimension = "Life satisfaction", 
                               get_dat(fit_life_sat))
make_graph(dat_fig_life_sat, "Life Satisfaction", 1, 10)
```

### Positive affect

Let's next expect the development across waves. 

```{r}
model_aff_pos <- lmer(aff_pos_m ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_aff_pos)
dat_fig_aff_pos <- data.frame(type = "Affect", dimension = "Positive", 
                              get_dat(model_aff_pos))
make_graph(dat_fig_aff_pos, "Positive Affect", 1, 5)
```

Positive affect was measured as a scale. We hence also inspect factorial validity using CFA. 

We first test assumption of multivariate normality. We focus on wave 1 here.

```{r}
d_long_100_imp %>%
  filter(wave == 1) %>% 
  select(aff_pos_1, aff_pos_2, aff_pos_3) %>% 
  mardia()
```

Assumption of multivariate normal distribution was violated; hence, robust estimator will be used.

```{r}
model <- "
aff_pos =~ a1*aff_pos_1 + a2*aff_pos_2 + a3*aff_pos_3
"
cfa_aff_pos <- cfa(model, d_long_100_imp, group = "wave", estimator = "MLM")
summary(cfa_aff_pos, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

The data fit the model very well, `r td::fit_txt(cfa_aff_pos)`.
Let's next inspect reliability.

```{r}
rel_aff_pos <- get_rel(cfa_aff_pos)
```

The average reliability across all waves was omega = `r rel_aff_pos[[1]]`, hence good.

Let's now export factor scores for results reported in additional analyses.

```{r}
# with imputed data
cfa_aff_pos_50 <- cfa(model, d_long_50_imp, group = "wave", estimator = "MLM")
d_long_50_imp$aff_pos_fs <- get_fs(cfa_aff_pos_50)

# without imputed data
cfa_aff_pos <- cfa(model, d_long_50, group = "wave", estimator = "MLM")
d_long_50$aff_pos_fs <- get_fs(cfa_aff_pos)
```

### Negative affect

```{r}
model_aff_neg <- lmer(aff_neg_m ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_aff_neg)
dat_fig_aff_neg <- data.frame(type = "Affect", dimension = "Negative", get_dat(model_aff_neg))
make_graph(dat_fig_aff_neg, "Negative Affect", 1, 5)
```

Negative affect was measured as a scale. We hence inspect factorial validity using CFA.

We first test assumption of multivariate normality. We'll focus on wave 1 here.

```{r eval=T}
d_long_100_imp %>%
  filter(wave == 1) %>% 
  select(aff_neg_1, aff_neg_2, aff_neg_3, aff_neg_4, aff_neg_5, aff_neg_6) %>% 
  mardia()
```

Assumption of multivariate normal distribution was violated; hence, robust estimator will be used.

```{r}
model <- "
aff_neg =~ a1*aff_neg_1 + a2*aff_neg_2 + a3*aff_neg_3 + a4*aff_neg_4 + a5*aff_neg_5 + a6*aff_neg_6
"
cfa_aff_neg <- cfa(model, d_long_100_imp, group = "wave", estimator = "MLM")
summary(cfa_aff_neg, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

The data fit the model very well, `r td::fit_txt(cfa_aff_neg)`.

Let's next inspect reliability.

```{r}
rel_aff_neg <- get_rel(cfa_aff_neg)
```

The average reliability across all waves was omega = `r rel_aff_neg[[1]]`, hence good.

```{r}
model_aff_neg <- lmer(aff_neg_m ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_aff_neg)
```

Let's now export factor scores, necessary for results reported in additional analyses.

```{r}
# with imputed data
cfa_aff_neg_50 <- cfa(model, d_long_50_imp, group = "wave", estimator = "MLM")
d_long_50_imp$aff_neg_fs <- get_fs(cfa_aff_neg_50)

# without imputed data
cfa_aff_neg <- cfa(model, d_long_50, group = "wave", estimator = "MLM")
d_long_50$aff_neg_fs <- get_fs(cfa_aff_neg)
```

## Social media use

Social media use (and channels) were measured at waves 1, 2, 8, 17, 23, 28, and for everyone who was newly recruited during the study at the first wave.

### Reading

```{r}
model_soc_med_read <- lmer(soc_med_read ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_read)
dat_fig_soc_med_read <- data.frame(type = "Social media use", dimension = "Reading", 
                                   get_dat(model_soc_med_read))
make_graph(dat_fig_soc_med_read, "Social Media Reading", 1, 5)
```

### Liking & sharing

```{r}
model_soc_med_like_share <- lmer(soc_med_like_share ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_like_share)
dat_fig_soc_med_like_share <- data.frame(type = "Social media use", dimension = "Liking & Sharing",
                                         get_dat(model_soc_med_like_share))
make_graph(dat_fig_soc_med_like_share, "Social Media Liking and Sharing", 1, 5)
```

### Posting

```{r}
model_soc_med_post <- lmer(soc_med_post ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_post)
dat_fig_soc_med_post <- data.frame(type = "Social media use", dimension = "Posting", 
                                   get_dat(model_soc_med_post))
make_graph(dat_fig_soc_med_post, "Social Media Posting", 1, 5)
```

## Social media channels
### Facebook

```{r}
model_soc_med_fb <- lmer(soc_med_fb ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_fb)
dat_fig_soc_med_fb <- data.frame(type = "Social media channel", dimension = "Facebook", 
                                 get_dat(model_soc_med_fb))
make_graph(dat_fig_soc_med_fb, "Social Media Facebook", 1, 5)
```

### Twitter

```{r}
model_soc_med_tw <- lmer(soc_med_tw ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_tw)
dat_fig_soc_med_tw <- data.frame(type = "Social media channel", dimension = "Twitter", 
                                 get_dat(model_soc_med_tw))
make_graph(dat_fig_soc_med_tw, "Social Media Twitter", 1, 5)
```

Interestingly, lme4 throws a warning, likely because there is too little variance across waves, while little variation measure itself. Let's inspect the raw means.

```{r}
soc_med_tw_m <- 
  d_long_100_imp %>% 
  group_by(wave) %>% 
  summarise(value = mean(soc_med_tw, na.rm = T))
soc_med_tw_m
```

Inspecting the means shows that the data are intact, only that the estimation didn't fully work.

### Instagram

```{r}
model_soc_med_ig <- lmer(soc_med_ig ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_ig)
dat_fig_soc_med_ig <- data.frame(type = "Social media channel", dimension = "Instagram", 
                                 get_dat(model_soc_med_ig))
make_graph(dat_fig_soc_med_ig, "Social Media Instagram", 1, 5)
```

### WhatsApp

```{r}
model_soc_med_wa <- lmer(soc_med_wa ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_wa)
dat_fig_soc_med_wa <- data.frame(type = "Social media channel", dimension = "WhatsApp", 
                                 get_dat(model_soc_med_wa))
make_graph(dat_fig_soc_med_wa, "Social Media WhatsApp", 1, 5)
```

### YouTube

```{r}
model_soc_med_yt <- lmer(soc_med_yt ~ (1 | id) + (1 | wave), d_long_100_imp)
summary(model_soc_med_yt)
dat_fig_soc_med_yt <- data.frame(type = "Social media channel", dimension = "YouTube", 
                                 get_dat(model_soc_med_yt))
make_graph(dat_fig_soc_med_yt, "Social Media YouTube", 1, 5)
```

## Locus of control

The only other variable that was measured as a scale was Locus of Control. Below I hence report the scale's factorial validity. Waves for which not a sufficient number of respondents took part were excluded.

```{r eval=T}
model <- "
loc_cntrl_int =~ a1*loc_cntrl_int_1 + a2*loc_cntrl_int_2 + a3*loc_cntrl_int_3 + a4*loc_cntrl_int_4
# loc_cntrl_int_1 ~~ loc_cntrl_int_2
loc_cntrl_int_3 ~~ loc_cntrl_int_4
"
cfa_loc_cntrl_int <- cfa(model, 
                         filter(d_long_100_imp, wave != 11, wave != 20,  wave != 26, wave != 27, wave != 29, wave != 31, wave != 32),
                         # d_long_100_imp,
                         group = "wave")
summary(cfa_loc_cntrl_int, standardized = TRUE, fit = TRUE, estimates = FALSE)
```

The data fit the model very well, `r td::fit_txt(cfa_loc_cntrl_int)`.

## Table

Table with descriptives of main variables.

```{r}
tab_desc_dat <- rbind(
    "Life satisfaction" = get_specs(fit_life_sat),
    "Positive affect" = get_specs(model_aff_pos),
    "Negative affect" = get_specs(model_aff_neg),
    "Read" = get_specs(model_soc_med_read),
    "Like & share" = get_specs(model_soc_med_like_share),
    "Posting" = get_specs(model_soc_med_post),
    "Facebook" = get_specs(model_soc_med_fb),
    "Twitter" = c(sd = get_specs(model_soc_med_tw)$sd,
                  min = min(soc_med_tw_m$value, na.rm = TRUE),
                  max = max(soc_med_tw_m$value, na.rm = TRUE),
                  mean = mean(soc_med_tw_m$value, na.rm = TRUE)
                  ),
    "Instagram" = get_specs(model_soc_med_ig),
    "WhatsApp" = get_specs(model_soc_med_wa),
    "YouTube" = get_specs(model_soc_med_yt)
    ) %>%
  as.data.frame()
tab_desc_dat
```

## Figure

Display the developments of all variables in a combined figure.

```{r}
fig_desc_dat <- data.frame(
  rbind(
    dat_fig_life_sat,
    dat_fig_aff_pos,
    dat_fig_aff_neg,
    dat_fig_soc_med_read,
    dat_fig_soc_med_like_share,
    dat_fig_soc_med_post,
    dat_fig_soc_med_fb,
    dat_fig_soc_med_tw,
    dat_fig_soc_med_ig,
    dat_fig_soc_med_wa,
    dat_fig_soc_med_yt
  ) %>% 
    mutate(
      type = factor(.$type, levels = c("Life satisfaction", "Affect", "Social media use", "Social media channel")),
      dimension = factor(.$dimension, levels = c("Life satisfaction", "Positive", "Negative", "Reading", "Liking & Sharing", "Posting", "Facebook", "Twitter", "Instagram", "WhatsApp", "YouTube"))
      )
)

fig_desc_life_sat <- make_graph(
  fig_desc_dat %>% filter(type == "Life satisfaction"), 
  title = "Life satisfaction", 
  ll = 0, ul = 10, 
  lmer = FALSE, 
  line = TRUE,
  legend = FALSE,
  points = FALSE
  )

fig_desc_aff <- make_graph(
  fig_desc_dat %>% filter(type == "Affect"), 
  title = "Affect", 
  ll = 1, ul = 5, 
  lmer = FALSE, 
  line = TRUE,
  points = FALSE,
  legend = TRUE
  )

fig_desc_soc_med_use <- make_graph(
  fig_desc_dat %>% filter(type == "Social media use"), 
  title = "Social media use", 
  ll = 1, ul = 5, 
  lmer = FALSE, 
  line = TRUE,
  points = FALSE,
  legend = TRUE
  )

fig_desc_soc_med_channel <- make_graph(
  fig_desc_dat %>% filter(type == "Social media channel"), 
  title = "Social media channel", 
  ll = 1, ul = 5, 
  lmer = FALSE, 
  line = TRUE,
  points = FALSE,
  legend = TRUE
  )

fig_desc <- grid.arrange(fig_desc_life_sat, fig_desc_aff, 
                         fig_desc_soc_med_use, fig_desc_soc_med_channel,
                         nrow = 2, ncol = 2)

ggsave("figures/fig_descriptives.png", 
       width = 10, height = 5,
       plot = fig_desc)
```

# Analyses

## Multicollinearity

Before running the analyses, let's briefly check zero-order correlation matrix, to get general picture and also for potential multicollinearity. We use variables from T1.

Multicollinearity will then also be checked explicitly in each analysis.

```{r eval=T}
d_long_100_imp %>% 
  filter(wave == 1) %>% 
  select(life_sat, aff_neg_m, aff_pos_m,
         soc_med_read, soc_med_post, soc_med_like_share, 
         soc_med_fb, soc_med_ig, soc_med_tw, soc_med_wa, soc_med_yt,
         health, corona_pos, work_h, work_homeoff, hh_income, med_txt_kro, med_txt_sta, med_txt_pre, med_txt_oes, med_txt_kur, med_txt_slz, med_txt_son, med_vid_orf, med_vid_pri, med_txt_kro, med_txt_sta, med_txt_pre, med_txt_oes, med_txt_kur, med_txt_slz, med_txt_son, med_vid_orf, med_vid_pri, act_wrk, act_spo, act_frn, act_sho, act_pet, risk_prop, loc_cntrl_int_m, sat_dem) %>% 
  cor(use = "pairwise.complete.obs") %>% 
  as.data.frame()
```

## Correlations

Let's also briefly look at bivariate relations between the types and channels of social media use and the well-being facets.

### Table

```{r}
dat_cor <- 
  d_long_100_mim %>% 
  filter(wave == 1) %>%  # we can use wave 1 only, because mean values are the same across waves
  select(`Life satis-\nfaction` = life_sat_b, 
         `Affect\npositive` = aff_pos_m_b, 
         `Affect\nnegative` = aff_neg_m_b,
         `Reading` = soc_med_read_b, 
         `Posting` = soc_med_post_b, 
         `Like &\nshare` = soc_med_like_share_b, 
         `Facebook` = soc_med_fb_b, 
         `Instagram` = soc_med_ig_b, 
         `Twitter` = soc_med_tw_b, 
         `WhatsApp` = soc_med_wa_b, 
         `YouTube` = soc_med_yt_b)
  # cor() %>% 
  # as.data.frame()
  # correlate() %>% 
  # fashion()

tab_cor <- 
  dat_cor %>% 
  correlate() %>% 
  fashion() %T>%
  print()
```

### Figure

```{r}
int_breaks <- function(x, n = 4) {
  l <- pretty(x, n)
  l[abs(l %% 1) < .Machine$double.eps ^ 0.5] 
}

fig_cor <- 
  dat_cor %>% 
  ggpairs(
    upper = list(continuous = cor_plot),
    lower = list(continuous = wrap("points", alpha = 0.3, size=0.1), 
              combo = wrap("dot", alpha = 0.3, size=0.1)),
    progress = FALSE
    ) + 
  scale_x_continuous(breaks = int_breaks) +
  theme_bw()

fig_cor
ggsave("figures/fig_cor.png", width = 8, height = 8)
```

## Publication
### Life satisfaction

```{r}
model_life_sat_lmer_pub <- "
  life_sat ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
    age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
    res_vienna + acc_bal + acc_gar + home_sqm + 
    corona_pos_b + corona_pos_w +
    work_h_b + work_h_w +
    work_homeoff_b +  work_homeoff_w +
    hh_income_b + hh_income_w +
    hh_adults + hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + 
    hh_oldfam + hh_outfam + hh_partner +
    home_owner +
    med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
    med_vid_orf_b + med_vid_pri_b + 
    med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + 
    med_vid_orf_w + med_vid_pri_w + 
    risk_prop_b + risk_prop_w + 
    act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
    act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
    sat_dem_w + sat_dem_b + 
    health_w + health_b +
    loc_cntrl_int_m_w + loc_cntrl_int_m_b
"
```

Let's first inspect multicollinearity.

```{r}
check_collinearity(lmerTest::lmer(model_life_sat_lmer_pub, d_long_100_imp))
```

No within-person predictor shows increased values for multicollinearity. Hence results straightforward.

Let's next inspect results of within-person predictors. Only parts of model shown to save space.

```{r}
fit_life_sat_lmer_pub <- with(d_long_100_mim_mice, exp = lmerTest::lmer(model_life_sat_lmer_pub))
fit_life_sat_lmer_pub <- summary(pool(fit_life_sat_lmer_pub), conf.int = TRUE)
print_res(fit_life_sat_lmer_pub)
```

### Positive Affect

```{r}
model_aff_pos_lmer_pub <- "
  aff_pos_m ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
    age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
    res_vienna + acc_bal + acc_gar + home_sqm + 
    corona_pos_b + corona_pos_w +
    work_h_b + work_h_w +
    work_homeoff_b +  work_homeoff_w +
    hh_income_b + hh_income_w +
    hh_adults + hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + 
    hh_oldfam + hh_outfam + hh_partner +
    home_owner +
    med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
    med_vid_orf_b + med_vid_pri_b + 
    med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + 
    med_vid_orf_w + med_vid_pri_w + 
    risk_prop_b + risk_prop_w + 
    act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
    act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
    sat_dem_w + sat_dem_b + 
    health_w + health_b +
    loc_cntrl_int_m_w + loc_cntrl_int_m_b
"
```

Let's first inspect multicollinearity.

```{r}
check_collinearity(lmerTest::lmer(model_aff_pos_lmer_pub, d_long_100_imp))
```

No within-person predictors show multicollinear relations.

In what follows, the results of within-person predictors.

```{r}
fit_aff_pos_lmer_pub <- with(d_long_100_mim_mice, exp = lmerTest::lmer(model_aff_pos_lmer_pub))
fit_aff_pos_lmer_pub <- summary(pool(fit_aff_pos_lmer_pub), conf.int = TRUE)
print_res(fit_aff_pos_lmer_pub)
```

### Negative Affect

```{r}
model_aff_neg_lmer_pub <- "
  aff_neg_m ~ 
    (1 | id) + (1 | wave) + 
    soc_med_read_w + soc_med_like_share_w + soc_med_post_w  + 
    soc_med_fb_w + soc_med_ig_w + soc_med_wa_w + soc_med_yt_w + soc_med_tw_w +
    soc_med_read_b + soc_med_like_share_b + soc_med_post_b + 
    soc_med_fb_b + soc_med_ig_b + soc_med_wa_b + soc_med_yt_b + soc_med_tw_b +  
    age + male + born_aus + born_aus_prnts + edu_fac + employment_fac +
    res_vienna + acc_bal + acc_gar + home_sqm + 
    corona_pos_b + corona_pos_w +
    work_h_b + work_h_w +
    work_homeoff_b +  work_homeoff_w +
    hh_income_b + hh_income_w +
    hh_adults + hh_child18 + hh_child17 + hh_child14 + hh_child5 + hh_child2 + 
    hh_oldfam + hh_outfam + hh_partner +
    home_owner +
    med_txt_kro_b + med_txt_sta_b + med_txt_pre_b + med_txt_oes_b + med_txt_kur_b + med_txt_slz_b + med_txt_son_b + 
    med_vid_orf_b + med_vid_pri_b + 
    med_txt_kro_w + med_txt_sta_w + med_txt_pre_w + med_txt_oes_w + med_txt_kur_w + med_txt_slz_w + med_txt_son_w + 
    med_vid_orf_w + med_vid_pri_w + 
    risk_prop_b + risk_prop_w + 
    act_wrk_w + act_spo_w + act_frn_w + act_sho_w + act_pet_w + 
    act_wrk_b + act_spo_b + act_frn_b + act_sho_b + act_pet_b +
    sat_dem_w + sat_dem_b + 
    health_w + health_b +
    loc_cntrl_int_m_w + loc_cntrl_int_m_b
"
```

Let's inspect multicollinearity.

```{r}
check_collinearity(lmerTest::lmer(model_aff_neg_lmer_pub, d_long_100_imp))
```

No within-person predictors show multicollinear relations.

Here are the results for the within-person predictors.

```{r}
fit_aff_neg_lmer_pub <- with(d_long_100_mim_mice, exp = lmerTest::lmer(model_aff_neg_lmer_pub))
fit_aff_neg_lmer_pub <- summary(pool(fit_aff_neg_lmer_pub), conf.int = TRUE)
print_res(fit_aff_neg_lmer_pub)
```

## Standardized results

Then let's report also the standardized results. Helps compare effect sizes across differently scaled predictors.

### Life satisfaction

```{r}
fit_life_sat_lmer_std <- with(d_long_100_mim_mice_std, exp = lmerTest::lmer(model_life_sat_lmer_pub))
fit_life_sat_lmer_std <- summary(pool(fit_life_sat_lmer_std), conf.int = TRUE)
print_res(fit_life_sat_lmer_std)
```

### Positive Affect

```{r}
fit_aff_pos_lmer_std <- with(d_long_100_mim_mice_std, exp = lmerTest::lmer(model_aff_pos_lmer_pub))
fit_aff_pos_lmer_std <- summary(pool(fit_aff_pos_lmer_std), conf.int = TRUE)
print_res(fit_aff_pos_lmer_std)
```

### Negative Affect

```{r}
fit_aff_neg_lmer_std <- with(d_long_100_mim_mice_std, exp = lmerTest::lmer(model_aff_neg_lmer_pub))
fit_aff_neg_lmer_std <- summary(pool(fit_aff_neg_lmer_std), conf.int = TRUE)
print_res(fit_aff_neg_lmer_std)
```

## Table

Let's extract results for a table of within-person effects.

```{r cache=F, eval=T}
tab_within <-
  data_tab_std %>% 
  filter(Type %in% c("Activity", "Channels")) %>% 
  select(std = estimate) %>% 
  cbind(data_tab_within) %>% 
  mutate(p.value = td::my_round(p.value, "p")) %>% 
  arrange(dv) %>% 
  select(Outcome = dv,
         Predictor = iv,
         b = estimate,
         `Lower` = conf.low,
         `Higher` = conf.high,
         beta = "std",
         p = "p.value")

tab_within
```

## Figures

Let's visualize results. First, results of unstandardized predictors.

```{r warning=F, cache=F}
# get dat
data_tab_within <- rbind(
  get_dat_res(fit_aff_neg_lmer_pub, fit_aff_pos_lmer_pub, fit_life_sat_lmer_pub, 
              type = "Activity", variance = "within", analysis = "Publication"),
  get_dat_res(fit_aff_neg_lmer_pub, fit_aff_pos_lmer_pub, fit_life_sat_lmer_pub, 
              type = "Channels", variance = "within", analysis = "Publication")
  )

# make fig
fig_results_within <- make_graph_res(
  data = data_tab_within,
  sesoi = "est",
  legend = FALSE
  , facet = "type"
  # , title = "Results of selected covariates"
  )
fig_results_within

# save figure
ggsave("figures/fig_results_within.png", 
       width = 7, height = 4,
       plot = fig_results_within)
```

Let's next visualize standardized predictors, to allow for better comparison across differently scaled variables.

```{r warning=F, cache=F, fig.height=7}
# make figure
data_tab_comp <- rbind(
  get_dat_res(fit_aff_neg_lmer_std, fit_aff_pos_lmer_std, fit_life_sat_lmer_std, 
              type = "Activity", variance = "within", analysis = "standardized"),
  get_dat_res(fit_aff_neg_lmer_std, fit_aff_pos_lmer_std, fit_life_sat_lmer_std, 
              type = "Channels", variance = "within", analysis = "standardized"),
  get_dat_res(fit_aff_neg_lmer_std, fit_aff_pos_lmer_std, fit_life_sat_lmer_std, 
              type = "News\nuse", variance = "within", analysis = "standardized"),
  get_dat_res(fit_aff_neg_lmer_std, fit_aff_pos_lmer_std, fit_life_sat_lmer_std, 
              type = "Living\nconditions", variance = "within", analysis = "standardized"),
  get_dat_res(fit_aff_neg_lmer_std, fit_aff_pos_lmer_std, fit_life_sat_lmer_std, 
              type = "Outdoor\nactivities", variance = "within", analysis = "standardized"),
  get_dat_res(fit_aff_neg_lmer_std, fit_aff_pos_lmer_std, fit_life_sat_lmer_std, 
              type = "Psycho-\nlogy", variance = "within", analysis = "standardized")
  )

fig_results_comp <- make_graph_res(
  data = data_tab_comp,
  sesoi = "std",
  legend = FALSE
  , facet = "type"
  # , title = "Results of selected covariates"
  )
fig_results_comp

# save figure
ggsave("figures/fig_results_comp.png", 
       width = 7, height = 7,
       plot = fig_results_control_std)
```

# Save workspace

```{r cache=F}
save.image("data/workspace_2.RData")
```
