---
title: "Analyses Setup"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---
  
```{r knitr-setup, include=F}
set.seed(170819)
knitr::opts_chunk$set(warning=F, echo=T, error=F, message=F, cache=T, rows.print=20)
options(digits=2, width=260, scipen=999)
```

- Here you can find the set-up for the analyses and the results.
- Includes custom functions, data-wrangling, and data imputation. 
- To see the code, click on button "Code".
- Alternatively, you can download the rmd file from the github repo.
- The data are hosted on aussda. Please download them separately, to rerun the analyses (https://doi.org/10.11587/28KQNS). 
- Note that this paper uses a scientific use file, which is at the time of writing not officially published.

# Set-up

Load packages.

```{r r-setup, results='hide', cache=F}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
packages <- c("broom.mixed", "brms", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", #"mvnormalTest", 
              "PerFit", "performance", "psych", "quanteda.textstats", "semTools", "tidyverse")

# load packages
lapply(c(packages, "td"), library, character.only = TRUE)
```

## Session info

Provide session info to make results reproducible.

```{r}
sessionInfo()
```

# Custom functions

## find_var

Find variables in dataset.

```{r}
find_var <- function(name, data = doc)(
  # finds the variables names for an item for each wave
  data %>%
    filter(Label == name) %>%
    select(Variable) %>%
    unlist() %>%
    set_names(sub("\\_.*", "", .))
)
```

## get_specs

Extract characteristics from fitted lmer models.

```{r}
get_specs <- function(model){
  # Get mean, max, and min values
  
  dat <- coefficients(model)$wave
  specs <- data.frame(
    sd = attr(VarCorr(model), "sc"),
    min = min(dat),
    max = max(dat),
    mean = mean(dat$`(Intercept)`)
  )
}
```

## get_dat

Get data from fitted lmer objects for descriptives.

```{r}
get_dat <- function(model){
  coefficients(model)$wave %>% 
    tibble::rownames_to_column("wave") %>% 
    rename(value = "(Intercept)") %>% 
    mutate(wave = as.integer(.$wave),
           value = as.numeric(.$value)) 
} 
```

## get_rel

Determine average reliability for measures across waves

```{r}
get_rel <- function(data, waves=24){
  
  # extract average reliability from lavaan fitted cfa with several groups
  reliability(data) %>% 
    unlist() %>% 
    matrix(5, waves) %>% 
    as.data.frame() %>% 
    set_rownames(c("alpha", "omega", "omega2", "omega3", "avevar")) %>% 
    summarise(omega = rowMeans(.["omega",])) %>% 
    return()
}
```

## make_graph

Make graph of variables' development.

```{r}
make_graph <- function(model, title, ll, ul, line = TRUE, points = TRUE, labels = FALSE, lmer=FALSE, legend=FALSE){

    if(isTRUE(lmer)){
      dat <- get_dat(model)
    } else{
    dat <- model
  }
    
  graph <- 
    ggplot(dat, aes(wave, value, color = dimension)) +
    {if(legend) theme(
      legend.position = c(0.85, 0.8),
      legend.title = element_blank()
      )} + 
    {if(!legend) theme(
      legend.position = "none"
    )} +
    theme(axis.title.x=element_blank()) +
    coord_cartesian(ylim = c(ll, ul)) +
    ggtitle(title) +
    {if(line) geom_smooth(se = FALSE, method = 'loess')} +
    {if(points) geom_point()} +
    scale_color_manual(values=c("dodgerblue3", "deepskyblue2", "magenta2", "green2", "red"))
  graph
}
```

## print_res

```{r}
# print results for online material
print_res <- function(object, imputation = TRUE){
  
  if(isTRUE(imputation)){
    object %>% 
      as.data.frame %>% 
      select(term, estimate, `2.5 %`, `97.5 %`, p.value) %>% 
      mutate(p.value = td::my_round(p.value, "p"))
    }
  else{
    object %>% 
      as.data.frame %>% 
      select(term, estimate, `2.5 %` = conf.low, `97.5 %` = conf.high, p.value) %>% 
      mutate(p.value = td::my_round(p.value, "p"))
  }
}
```

## get_dat_res

Get data of lmer objects for specific results.

```{r}
# get data
get_dat_res <- function(data_aff_neg, data_aff_pos, data_life_sat, variance = "within", type = "channels", analysis = "Standardized"){
  
  if(isTRUE(class(data_aff_neg) == "lmerModLmerTest")) {
         dat_fig_results <- 
           broom.mixed::tidy(data_aff_neg, conf.int = T) %>% 
           mutate(dv = "aff_neg") %>% 
           rbind(
             broom.mixed::tidy(data_aff_pos, conf.int = T) %>% 
               mutate(dv = "aff_pos")) %>% 
           rbind(
             broom.mixed::tidy(data_life_sat, conf.int = T) %>% 
               mutate(dv = "life_sat"))
         } else{ 
           dat_fig_results <- 
             data_aff_neg %>% 
             mutate(dv = "aff_neg") %>% 
             rbind(data_aff_pos %>% 
                   mutate(dv = "aff_pos")) %>% 
             rbind(data_life_sat %>% 
                     mutate(dv = "life_sat")) %>% 
           rename(conf.low = `2.5 %`, conf.high = `97.5 %`)
           }
  dat_fig_results %<>% 
  mutate(
    Variance = ifelse(grepl(".*_w\\>", .$term), "within", "between"),
    iv = gsub("_(w|b)\\>", "", .$term)
         ) %>%
  mutate(
    Variance = factor(.$Variance, 
                  levels = c("within", "between")),
    dv = factor(.$dv, 
                levels = c("life_sat", "aff_pos", "aff_neg"),
                labels = c("Life satisfaction", "Positive affect", "Negative affect")),
    Type = type,
    Analysis = analysis
  ) %>% 
  select(dv, iv, Variance, Type, Analysis, estimate, conf.low, conf.high, p.value) %>% 
    filter(Variance == variance)

  # select Social Media type of activity
  if(type == "Activity") {
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_read", "soc_med_like_share", "soc_med_post")) %>% 
    mutate(
      iv = factor(.$iv, 
                  levels = c("soc_med_post", "soc_med_like_share", "soc_med_read"), 
                  labels = c("Posting", "Liking & Sharing", "Reading"))
    )
  } else if(type == "Channels"){
    dat_fig_results %<>%
    filter(iv %in% c("soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")) %>% 
    mutate(iv = factor(.$iv, levels = c("soc_med_yt", "soc_med_wa", "soc_med_ig", "soc_med_tw", "soc_med_fb"), labels = c("YouTube", "WhatsApp", "Instagram", "Twitter", "Facebook")))
  } else if(type == "Controls"){
    dat_fig_results %<>%
      filter(iv %in% c("male", "health", "loc_cntrl_int_m",
                       "act_spo", "sat_dem", "corona_pos")) %>% 
      mutate(iv = factor(.$iv, levels = c("male", "health", "loc_cntrl_int_m",
                                          "act_spo", "sat_dem", "corona_pos"), 
                         labels = c("Male", "Health", "Internal locus of control",
                                    "Sport", "Satisfaction democracy", "Corona positive")))
  } else if(type == "Living\nconditions"){
    dat_fig_results %<>%
      filter(iv %in% c("health", "corona_pos", "work_h", "work_homeoff", "hh_income")) %>% 
      mutate(iv = factor(.$iv, levels = c("health", "corona_pos", "work_h", "work_homeoff", "hh_income"),
                         labels = c("Health", "Corona positive", "Work hours", "Homeoffice", "Household income")))
  } else if(type == "News\nuse"){
    dat_fig_results %<>%
      filter(iv %in% c("med_txt_kro", "med_txt_sta", "med_txt_pre", "med_txt_oes", "med_txt_kur", "med_txt_slz", "med_txt_son", "med_vid_orf", "med_vid_pri")) %>% 
      mutate(iv = factor(.$iv, levels = c("med_txt_kro", "med_txt_sta", "med_txt_pre", "med_txt_oes", "med_txt_kur", "med_txt_slz", "med_txt_son", "med_vid_orf", "med_vid_pri"),
                         labels = c("Krone", "Der Standard", "Die Presse", "Österreich", "Kurier", "Salzb. Nachrichten", "Other", "ORF", "Private news")))
  } else if(type == "Outdoor\nactivities"){
    dat_fig_results %<>%
      filter(iv %in% c("act_wrk", "act_spo", "act_frn", "act_sho", "act_pet")) %>% 
      mutate(iv = factor(.$iv, levels = c("act_wrk", "act_spo", "act_frn", "act_sho", "act_pet"),
                         labels = c("Working", "Sports", "Friends", "Shopping", "With pets")))
  } else if(type == "Psycho-\nlogy"){
    dat_fig_results %<>%
      filter(iv %in% c("risk_prop", "loc_cntrl_int_m", "sat_dem")) %>% 
      mutate(iv = factor(.$iv, levels = c("risk_prop", "loc_cntrl_int_m", "sat_dem"),
                         labels = c("Risk taking", "Internal locus of control", "Satisfaction democracy")))
  }
  return(dat_fig_results)
}
```

## make_graph_res

Make graph of effects

```{r}
make_graph_res <- function(data, sesoi = NULL, legend = TRUE, facet = "type", title = NULL){
  ggplot(data, aes(x = estimate, y = iv)) + 
  scale_color_manual(values = c("black", "grey75", "darkcyan", "deepskyblue", "cornflowerblue", "darkcyan", "aquamarine")) +
  geom_vline(xintercept = 0, lwd = .75, colour = "darkgrey") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high, color = Analysis),
                lwd = .75, height = .2, position = position_dodge(-.7)) +
  geom_point(aes(color = Analysis), size = 1.5, position = position_dodge(-.7)) +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=-.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv=="Life satisfaction"), aes(xintercept=.3), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=-.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "est")) geom_vline(data=filter(data, dv!="Life satisfaction"), aes(xintercept=.15), colour="darkgrey", linetype = "dashed")} +
    {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=.1), colour="darkgrey", linetype = "dashed")} + 
    {if(isTRUE(sesoi == "std")) geom_vline(aes(xintercept=-.1), colour="darkgrey", linetype = "dashed")} +   
  theme(
    axis.title.y = element_blank(),
    plot.title = element_text(hjust = .5),
    panel.spacing = unit(.9, "lines"),
    text = element_text(size = 12),
    axis.text.y = element_text(hjust = 1)
    ) +
  {if(!is.null(title)) ggtitle(title)} +
  {if(!isTRUE(legend)) theme(legend.position = "none")} + 
  # guides(colour = guide_legend(reverse=T)) +
    {if(facet == "type")
      facet_grid(rows = vars(Type),
             cols = vars(dv),
             scales = "free",
             space = "free_y")
    } + 
    {if(facet == "analysis")
      facet_grid(rows = vars(Variance),
             cols = vars(dv),
             scales = "free",
             space = "free_y")
    }
}
```

## get_fs

Extract factor scores.

```{r}
get_fs <- function(model) {
  # the aim is to get factor scores on original scaling
  # hence export factor values for all items
  # then compute average
  dat_ov <- lavaan::lavPredict(model, type = "ov", assemble = TRUE) %>% 
    mutate(fs = rowMeans(.[1:3]))
  return(dat_ov$fs)
}
```

# Data Wrangling
## Load data

```{r}
doc <- read_csv2("data/Variable_List_w1-34.csv")
d_raw <- read_csv("data/W1-32_ACPP_V20220601.csv")
```

## Find names

Identify the names of each item for each wave.

```{r}
# identify variable names of items, using custom function
health <- find_var("Gesundheitszustand") # wsn't collected at wave 21
aff_neg_1 <- find_var("Depressivitaet: einsam")
aff_neg_2 <- find_var("Depressivitaet: aergerlich")
aff_neg_3 <- find_var("Depressivitaet: so niedergeschlagen")
aff_neg_4 <- find_var("Depressivitaet: sehr nervoes")
aff_neg_5 <- find_var("Depressivitaet: aengstlich")
aff_neg_6 <- find_var("Depressivitaet: bedrueckt und traurig")
aff_pos_1 <- find_var("Depressivitaet: ruhig und gelassen")
aff_pos_2 <- find_var("Depressivitaet: gluecklich")
aff_pos_3 <- find_var("Depressivitaet: voller Energie")
act_wrk <- find_var("Zuhause verlassen: Arbeit")
act_spo <- find_var("Zuhause verlassen: Sport")
act_frn <- find_var("Zuhause verlassen: Freunde oder Verwandte treffen")
act_sho <- find_var("Zuhause verlassen: Essen einkaufen")
act_pet <- find_var("Zuhause verlassen: Haustier ausfuehren")
sat_dem <- find_var("Demokratiezufriedenheit: Oesterreich")
work_h <- find_var("Arbeitsstunden: Jetzt pro Woche")
work_homeoff <- find_var("Aenderung berufliche Situation: Home-Office")
hh_income <- find_var("Aktuelles Haushaltseinkommen")
med_txt_kro <- find_var("Mediennutzung: Kronen Zeitung oder www.krone.at")
med_txt_sta <- find_var("Mediennutzung: Der Standard oder derstandard.at")
med_txt_pre <- find_var("Mediennutzung: Die Presse oder diepresse.com")
med_txt_oes <- find_var("Mediennutzung: Oesterreich oder oe24.at")
med_txt_kur <- find_var("Mediennutzung: Kurier oder kurier.at")
med_txt_slz <- find_var("Mediennutzung: Salzburger Nachrichten oder salzburg.at")
med_txt_son <- find_var("Mediennutzung: Sonstige oesterreichische Tageszeitungen")
med_vid_orf <- find_var("Mediennutzung: ORF (Nachrichten)")
med_vid_pri <- find_var("Mediennutzung: Privatfernsehen (Nachrichten)")
soc_med_fb <- find_var("Soziale Medien: Facebook")
soc_med_tw <- find_var("Soziale Medien: Twitter")
soc_med_ig <- find_var("Soziale Medien: Instagram")
soc_med_yt <- find_var("Soziale Medien: Youtube")
soc_med_wa <- find_var("Soziale Medien: WhatsApp")
soc_med_read <- find_var("Soziale Medien Aktivitaet: Postings zu Corona anderer lesen")
soc_med_like_share <- find_var("Soziale Medien Aktivitaet: Postings liken, teilen oder retweeten")
soc_med_post <- find_var("Soziale Medien Aktivitaet: selber Postings zu Corona verfassen")
life_sat <- find_var("Lebenszufriedenheit")
risk_prop <- find_var("Risikobereitschaft")
loc_cntrl_int_1 <- find_var("Psychologie: habe Leben selbst in der Hand")
loc_cntrl_int_2 <- find_var("Psychologie: Belohnung durch Anstrengung")
loc_cntrl_int_3 <- find_var("Psychologie: Fremdbestimmung")
loc_cntrl_int_4 <- find_var("Psychologie: Schicksal")
trst_media <- find_var("Vertrauen: ORF")
trst_police <- find_var("Vertrauen: Polizei")
trst_media <- find_var("Vertrauen: Parlament")
trst_hlthsec <- find_var("Vertrauen: Gesundheitswesen")
trst_gov <- find_var("Vertrauen: Bundesregierung")
trst_army <- find_var("Vertrauen: Bundesheer")
corona_pos <- c(
  find_var("Corona-Diagnose: Respondent"),
  find_var("Corona-Diagnose: Monat")
)
```

## Select variables

```{r}
d_wide <- d_raw %>% 
  select(
    id = RESPID,
    gender = SD_GENDER,
    acc_bal = SD_ACCESS_BALCONY,
    acc_gar = SD_ACCESS_GARDEN,
    year_birth = SD_BIRTHYEAR,
    born_aus = SD_BORN_AUSTRIA,
    born_aus_prnts = SD_MIGR_BACKGR,
    county = SD_BULA,
    edu = SD_EDU,
    employment = SD_EMPLSTATUS_FEB2020,
    hh_adults = SD_HH_ADULTS,
    hh_child18 = SD_HH_CHILD18,
    hh_child17 = SD_HH_TEENS,
    hh_child14 = SD_HH_CHILD14,
    hh_child5 = SD_HH_CHILD5,
    hh_child2 = SD_HH_CHILD2,
    hh_oldfam = SD_HH_OLDERFAM,
    hh_outfam = SD_HH_OUTERFAM,
    hh_partner = SD_HH_PARTNER,
    # hh_income = SD_HHINCOME_FEB2020,
    home_sqm = SD_HOME_SQM,
    home_owner = SD_HOMEOWNER,
    # work_h = SD_WORKHOURS_FEB2020,
    health = all_of(health),
    life_sat = all_of(life_sat),
    aff_neg_1 = all_of(aff_neg_1),
    aff_neg_2 = all_of(aff_neg_2),
    aff_neg_3 = all_of(aff_neg_3),
    aff_neg_4 = all_of(aff_neg_4),
    aff_neg_5 = all_of(aff_neg_5),
    aff_neg_6 = all_of(aff_neg_6),
    aff_pos_1 = all_of(aff_pos_1),
    aff_pos_2 = all_of(aff_pos_2),
    aff_pos_3 = all_of(aff_pos_3),
    act_wrk = all_of(act_wrk),
    act_spo = all_of(act_spo),
    act_frn = all_of(act_frn),
    act_sho = all_of(act_sho),
    act_pet = all_of(act_pet),
    sat_dem = all_of(sat_dem),
    sat_dem = all_of(sat_dem),
    work_h = all_of(work_h),
    work_homeoff = all_of(work_homeoff),
    hh_income = all_of(hh_income),
    med_txt_kro = all_of(med_txt_kro),
    med_txt_sta = all_of(med_txt_sta),
    med_txt_pre = all_of(med_txt_pre),
    med_txt_oes = all_of(med_txt_oes),
    med_txt_kur = all_of(med_txt_kur),
    med_txt_slz = all_of(med_txt_slz),
    med_txt_son = all_of(med_txt_son),
    med_vid_orf = all_of(med_vid_orf),
    med_vid_pri = all_of(med_vid_pri),
    soc_med_fb = all_of(soc_med_fb),
    soc_med_tw = all_of(soc_med_tw),
    soc_med_ig = all_of(soc_med_ig),
    soc_med_yt = all_of(soc_med_yt),
    soc_med_wa = all_of(soc_med_wa),
    soc_med_like_share = all_of(soc_med_like_share),
    soc_med_read = all_of(soc_med_read),
    soc_med_post = all_of(soc_med_post),
    risk_prop = all_of(risk_prop),
    loc_cntrl_int_1 = all_of(loc_cntrl_int_1),
    loc_cntrl_int_2 = all_of(loc_cntrl_int_2),
    loc_cntrl_int_3 = all_of(loc_cntrl_int_3),
    loc_cntrl_int_4 = all_of(loc_cntrl_int_4),
    trst_media = all_of(trst_media),
    trst_police = all_of(trst_police),
    trst_media = all_of(trst_media),
    trst_hlthsec = all_of(trst_hlthsec),
    trst_gov = all_of(trst_gov),
    trst_army = all_of(trst_army),
    corona_pos = all_of(corona_pos)
  )
```

Make new documentation with selected variables.

```{r}
doc_selected <- filter(doc, Variable %in% c(
  "RESPID",
  "SD_GENDER",
  "SD_ACCESS_BALCONY",
  "SD_ACCESS_GARDEN",
  "SD_BIRTHYEAR",
  "SD_BORN_AUSTRIA",
  "SD_MIGR_BACKGR",
  "SD_BULA",
  "SD_EDU",
  "SD_EMPLSTATUS_FEB2020",
  "SD_HH_ADULTS",
  "SD_HH_CHILD18",
  "SD_HH_TEENS",
  "SD_HH_CHILD14",
  "SD_HH_CHILD5",
  "SD_HH_CHILD2",
  "SD_HH_OLDERFAM",
  "SD_HH_OUTERFAM",
  "SD_HH_PARTNER",
  "SD_HHINCOME_FEB2020",
  "SD_HOME_SQM",
  "SD_HOMEOWNER",
  "SD_WORKHOURS_FEB2020",
  health,
  life_sat,
  aff_neg_1,
  aff_neg_2,
  aff_neg_3,
  aff_neg_4,
  aff_neg_5,
  aff_neg_6,
  aff_pos_1,
  aff_pos_2,
  aff_pos_3,
  act_wrk,
  act_spo,
  act_frn,
  act_sho,
  act_pet,
  sat_dem,
  work_h,
  work_homeoff,
  hh_income,
  med_txt_kro,
  med_txt_sta,
  med_txt_pre,
  med_txt_oes,
  med_txt_kur,
  med_txt_slz,
  med_txt_son,
  med_vid_orf,
  med_vid_pri,
  soc_med_fb,
  soc_med_tw,
  soc_med_ig,
  soc_med_yt,
  soc_med_wa,
  soc_med_like_share,
  soc_med_post,
  soc_med_read,
  risk_prop,
  loc_cntrl_int_1,
  loc_cntrl_int_2,
  loc_cntrl_int_3,
  loc_cntrl_int_4,
  trst_media,
  trst_police,
  trst_media,
  trst_hlthsec,
  trst_gov,
  trst_army,
  corona_pos
))
write.csv(doc_selected, "data/documentation.csv")
```

## Recode variables

```{r}
d_wide %<>%
  mutate_at(vars(everything(.)), funs(na_if(., 88))) %>%
  mutate_at(vars(everything(.)), funs(na_if(., 99))) %>%
  mutate(
    male = 2 - .$gender,
    age = 2021 - .$year_birth,
    res_vienna = recode(.$county, `8` = 1L, .default = 0L,),
    born_aus = 2 - .$born_aus,
    home_owner = 2 - .$home_owner,
    employment_fac = factor(.$employment, 
                            labels = c("Unemployed",
                                       "Industrie",
                                       "Public service",
                                       "Self-employed",
                                       "Retired",
                                       "Housekeeping",
                                       "Student",
                                       "Incapacitated",
                                       "Parental Leave"),
                            levels = c(4, 1:3, 5:8, 10) # make unemployment reference cat
    ),
    edu_fac = factor(.$edu,
                     labels = c("No degree", 
                                "Middle school",
                                "Vocational school",
                                "Technical school",
                                "High school",
                                "Applied high school",
                                "State college",
                                "Bachelor",
                                "Master",
                                "PhD")
    ))
```

## Make long data format

```{r cache=T}
d_long <-
  d_wide %>% 
  pivot_longer(
    cols = health...W1:corona_pos...W32,
    names_to = "item",
    values_to = "value"
  ) %>% 
  separate(item, c("item", "wave"), sep = "\\.\\.\\.", extra = "merge") %>% 
  pivot_wider(names_from = "item", values_from = "value")
```

## Recode values

```{r}
# recode such that higher values imply more strength / align with wording
d_long %<>% 
  mutate_at(vars(med_txt_kro:med_vid_pri, health, sat_dem, soc_med_fb:soc_med_post), 
            funs(recode(., `1` = 5L, `2` = 4L, `3` = 3L, `4` = 2L, `5` = 1L))) %>% 
  mutate_at(vars(loc_cntrl_int_1:loc_cntrl_int_4), 
            funs(recode(., `1` = 4L, `2` = 3L, `3` = 2L, `4` = 1L))) %>% 
  mutate_at(vars(born_aus_prnts), 
            funs(recode(., `3` = 0L, `2` = 2L, `1` = 1L)))

# recode inverted items
d_long %<>%
  mutate_at(vars(loc_cntrl_int_3, loc_cntrl_int_4), 
            funs(recode(., `1` = 4L, `2` = 3L, `3` = 2L, `4` = 1L)))

# recode other
d_long %<>%
  mutate(
    wave = gsub("W", "", .$wave) %>% as.integer(),
    id = as.integer(id)
  )
```

## Order dataset

```{r}
d_long %<>%
  arrange(id, wave)
```

# Impute data

Next we impute data. Note that the actual imputation below is deactivated and loaded from memory to save time.

## Prep

Determine amount of missingness per respondent per wave. 

```{r}
vars_used <- c("life_sat", "aff_pos_1", "aff_pos_2", "aff_pos_3", "aff_neg_1", "aff_neg_2", "aff_neg_3", "aff_neg_4", "aff_neg_5", "aff_neg_6", "soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw", "age", "male", "born_aus", "born_aus_prnts", "edu_fac", "employment_fac", "health", "res_vienna", "acc_bal", "acc_gar", "home_sqm", "med_txt_kro", "med_txt_sta", "med_txt_pre", "med_txt_oes", "med_txt_kur", "med_txt_slz", "med_txt_son", "med_vid_orf", "med_vid_pri", "risk_prop", "loc_cntrl_int_1", "loc_cntrl_int_2", "loc_cntrl_int_3", "loc_cntrl_int_4", "act_wrk", "act_spo", "act_frn", "act_sho", "act_pet", "sat_dem", "trst_media", "trst_police", "trst_media", "trst_hlthsec", "trst_gov", "trst_army", "corona_pos") # only include vars measured at _all_ points
```

Filter respondents with more than 50% missing data -- only needed for analyses as originally preregistered (see additional analyses).

```{r eval=T}
d_long_50 <- 
  d_long %>% 
  mutate(na_perc = rowSums(is.na(select(., all_of(vars_used))) / ncol(select(., all_of(vars_used))))) %>% 
  filter(na_perc < .5)
write_csv(d_long_50, "data/data_50.csv")
```

Exclude social media use data, because they were measured only on selected waves.

```{r}
vars_excl <- c("soc_med_read", "soc_med_like_share", "soc_med_post", "soc_med_fb", "soc_med_ig", "soc_med_wa", "soc_med_yt", "soc_med_tw")
incl_ma <- d_long %>% 
  mutate(across(.cols = everything(), .fns = is.na))
incl_ma[vars_excl] <- FALSE

# now also for data where 50% missing excluded
incl_ma_50 <- d_long_50 %>% 
  mutate(across(.cols = everything(), .fns = is.na))
incl_ma_50[vars_excl] <- FALSE
```

## Single imputation

For analyses as originally preregistered (see additional analyses), hence only participants who provided more than 50% of all data.

```{r imputation-single-50, eval=F, cache=T}
d_long_50_imp <- mice(d_long_50, 
                      method = "pmm", # use predictive mean matching
                      m = 1, maxit = 30, # only 1 imputation
                      # where = incl_ma_50,
                      seed = 180719, print = FALSE)
d_long_50_imp <- mice::complete(d_long_50_imp)
write_csv(d_long_50_imp, "data/data_50_imputed.csv")
```

Because CFAs aren't evaluated with multiple imputation, impute single data-set. Missing data was imputed for everyone.

```{r imputation-single-100, eval=F, cache=T}
d_long_100_imp <- mice(d_long, 
                   method = "pmm", # use predictive mean matching
                   m = 1, maxit = 30, # only 1 imputation
                   # where = incl_ma,
                   seed = 180719, print = FALSE)
d_long_100_imp <- mice::complete(d_long_100_imp)
write_csv(d_long_100_imp, "data/data_100_imputed.csv")
```

## Multiple Imputation

Now, multiple imputation of data-sets (5 data sets, 5 iterations), used for the final analyses.

```{r imputation-mult, eval=F, cache=T}
# impute missing data with multiple imputation
d_long_100_mim_mice <- mice(d_long, 
                   method = "pmm", # use predictive mean matching
                   m = 5, maxit = 5, # 5 imputations, 5 iterations
                   # where = incl_ma,
                   seed = 180719, print = FALSE)
d_long_100_mim <- mice::complete(d_long_100_mim_mice, action = "long", include = TRUE)
write_csv(d_long_100_mim, "data/data_100_mim.csv")
```

## Load data

To increase speed, you can also load the imputed data from the directory

```{r eval=T}
d_long_50_imp <- read_csv("data/data_50_imputed.csv") # data where people with >50% missing data were filtered
d_long_100_imp <- read_csv("data/data_100_imputed.csv") # data where all people were included
d_long_100_mim <- read_csv("data/data_100_mim.csv") # data where all people were included
```

# Create within-between data

First, create means for scales. Then, create mean values for each person (between), and unique changes per wave (within).

```{r}
d_long_100_mim <-
  d_long_100_mim %>% 
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_100_mim %<>%
  group_by(id) %>% 
  mutate_at(vars(health:loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()

d_long_100_mim_mice <- as.mids(d_long_100_mim)
```

```{r}
d_long_100_imp <-
  d_long_100_imp %>% 
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_100_imp %<>%
  group_by(id) %>% 
  mutate_at(vars(health:corona_pos, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

And because later we want to rerun the results as originally preregistered, we'll now do the same for analyses without filtered data.

```{r}
d_long_50_imp <-
  d_long_50_imp %>% 
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_50_imp %<>% 
  group_by(id) %>% 
  mutate_at(vars(health:corona_pos, loc_cntrl_int_m), 
            funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

And because later we want to rerun the results without imputed data, now the same for data without imputation.

```{r}
d_long_50 %<>% 
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_50 %<>% 
  group_by(id) %>% 
  mutate_at(vars(health:corona_pos, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>% 
  ungroup()
```

And now the same for the standardized data set.

```{r}
d_long_100_mim_std <-
  d_long_100_mim %>% 
  group_by(.imp) %>% 
  mutate_at(vars(gender:corona_pos, -id, -wave, -gender, -male, -born_aus, -born_aus_prnts, -edu_fac, -employment_fac, -res_vienna, -acc_bal, -acc_gar), ~ c(scale(.))) %>% 
  ungroup()

d_long_100_mim_std %<>%
  mutate(aff_pos_m = rowMeans(select(., aff_pos_1 : aff_pos_3)),
         aff_neg_m = rowMeans(select(., aff_neg_1 : aff_neg_6)),
         loc_cntrl_int_m = rowMeans(select(., loc_cntrl_int_1 : loc_cntrl_int_4)))

d_long_100_mim_std %<>%
  group_by(id) %>%
  mutate_at(vars(health:corona_pos, loc_cntrl_int_m), funs(b = mean(., na.rm = TRUE), w = . - mean(., na.rm = TRUE))) %>%
  ungroup()

d_long_100_mim_mice_std <- as.mids(d_long_100_mim_std)
```

# Save workspace

```{r cache=F}
save.image("data/workspace_1.RData")
```
